\pdftitle

### 2017-07-30 rebuttal.txt

The author(s) thank the three reviewers for their feedback. Here are our replies point-by-point.

Reviewer 1 ("Assigned_Reviewer_1")

1. We agree that the introduction part did not give enough neuroscientific introductory context and literature. The maximum-entropy method at the "sample level" has actually been repeatedly used and analysed in computational neuroscience since the work of Bohte et al (2000) to the present. A more complete bibliography is given at the end of this response and can be easily extended. The method is also used by non-experts, and our point would be to clarify some assumptions implicit the method also for non-experts.

2. The reviewer is again right. Our discussion starts from the *constatation* that most of the neuroscientific literature implicitly or explicitly generalizes the statistical properties of a sample of recorded neurons, analysed via maximum-entropy, to whole areas the neurons are recorded from, eg retina or motor cortex. This generalization is a complex argument lying outside our competence; we cannot justify or deprecate it in this manuscript. Our purpose is to warn neuroscientists who make this generalization: the typical sample-level method commonly used in the literature is inconsistent with this generalization. We are proposing a more consistent approach.

The case of absolute ignorance (I'') is not used in the rest of the manuscript and was confusing; we would omit it in a revised version.

We invite the reviewer to read also our responses 1 & 2 to the second reviewer.

3. We again agree: our principal equations are:

(15) to be used when a larger population is assumed and its size roughly known;

(17) *the equation used in the literature*, to be used when no larger population is assumed;

(19) to be used when the the size of the larger population is unknown.

Equations (15) and (19) are novel to our knowledge. Unfortunately we failed to emphasize these three equations and give clear guidance to their use. We would amend this in a revised version.

4. The captions should indeed give a clearer explanation of the figures. We would amend this in a revised version.

Reviewer 2 ("Assigned_Reviewer_2")

1. We agree with the reviewer, we did not give enough context and literature. Our starting point is indeed that

- the *sample-level* maximum-entropy method is increasingly being used in the neuroscientific literature (references below);

- this literature often generalizes results obtained by this method from a recorded sample to a whole area;

- worries have already been expressed (eg Ganmor et al 2011, Roudi et al PlosCB 2009) about the sample-size dependence of maximum-entropy results.

Our manuscript would like to explain from simple probability considerations why these worries are motivated, why the results depend on the sample size, and what alternative formulae can be used: eqns (15), (19).

2. The reviewer is right, we should have mentioned and referenced an important fact: the sample approach is routinely used in the literature. We agree that it is not an option if we assume sampling from a larger population. Our manuscript wanted to explain why it is not an option, and propose more valid alternatives (eqns 15, 19).

The phrase "left for future work" was unfortunate. Eqn (19), for unknown population size, can actually be used and numerically computed as is. Left for future work is the analysis of its mathematical properties. In a revised version of the paper we would add to each figure also the distribution obtained by eqn (19).

We invite the reviewer to read also our responses 1 & 2 to the first reviewer.

3. It is true, we give much space to the old formulae of sampling without replacement. This was on purpose, see lines 42-45: "The relations we present are well-known in survey sampling and in the pedagogic problem of drawing from an urn without replacement, yet they are somewhat hard to find explicitly written in the neuroscientific literature, so they may be of interest on their own". We should have stressed more that our manuscript wanted to "advertize" the importance of these formulae, not much used in neuroscience but very central to it.

4. Equation (12) and its discussion (lines 113-129) are irrelevant to the rest of the paper, to the discussion of maximum-entropy and to the main equations. We would eliminate this whole passage in a revised version.

5. We would have liked to present a Bayesian analysis of the problem, but the page limit prevented this; the manuscript could become confusing. In a revised version we would add a measure of discrepancy, eg Kullback-Leibler divergence, between the "sample" and "population" approach.

Reviewer 3 ("Assigned_Reviewer_5")

We cordially thank the reviewer for the appreciative words. We would modify the manuscript to address the concerns of the other reviewers but leaving the theoretical points. We want to add that our figures do use actual recorded neural activity data, but because of the double-blind review procedure we could not give more details and made comparison with recorded frequency distributions in the reviewed version.ÿ

Sample references of maximum-entropy use in neuroscientific literature:
Martignon & al, Biol Cybern (1995)
Bohte & al, Neural Comp (2000)
Schneidman & al,  Nature (2006)
Shlens & al,  J Neurosci (2006)
Tkačik & al, arXiv:q-bio/0611072 (2006)
Macke & al, Neural Comp (2009)
Roudi & al, PLoS CB (2009)
Roudi & al, Front Comp Neurosci (2009)
Roudi & al, Phys Rev E (2009)
Tkačik & al, arXiv:09125409 (2009)
Macke & al, Tech Rep (2009)
Gerwinn & al, Front Comput Neurosci (2010)
Barreiro & al, arXiv:10112797 (2010)
Macke & al, NIPS (2011)
Macke & al, Phys Rev Lett (2011)
Ganmor & al, Proc Natl Acad Sci (2011)
Granot-Atedgi & al, PLoS CB (2013)
Macke & al, Entropy (2013)
Tkačik & al, Proc Natl Acad Sci (2014)
Mora & al, Phys Rev Lett (2015)
Shimazaki & al,  Sci Rep (2015)

### 2017-07-30 rebuttal2.txt

The author(s) thank the three reviewers for their feedback, which is extremely useful for a revised version of the manuscript, even in case of non-acceptance. Here are our comments point-by-point.

Reviewer 1 ("Assigned_Reviewer_1")

1. The "sample level" maximum-entropy method has been repeatedly used and discussed in computational neuroscience since the work of Bohte et al (2000). A more complete bibliography is given at the end of this response and could be easily extended. Unfortunately our introduction did not clarify and reference this context enough; it would surely be amended in a revised version. The method is also used by non-experts; our purpose is to clarify some implicit assumptions that experts and non-experts seem to be unaware of.

2. Our discussion starts from an observation: in the neuroscientific literature some authors generalize conclusions drawn via maximum-entropy on a sample of recorded neurons, to whole areas the sample is recorded from, eg retina or motor cortex. Unfortunately this observation was not made clear in our introduction. Our purpose is to give a warning: the typical sample-level approach (Eq. 17) is incompatible with the beyond-sample generalizations made by some authors. We propose a simple alternative consistent with this assumption (Eqs 15, 19).

The case of absolute ignorance (I'') is not used in the rest of the manuscript; we apologize for the confusion it creates. We would omit it in a revised version.

We invite the reviewer to read also our responses 1 & 2 to the second reviewer.

3. In the manuscript the principal equations are:

(15) to be used when a larger population is assumed and its size roughly known;

(17) to be used when no larger population is assumed: most literature uses this equation but also assumes a larger population;

(19) to be used when the the size of the larger population is uncertain.

Equations (15) and (19) are novel, to our knowledge. Unfortunately we did not emphasize the role of these three equations and give clear guidance to their use. This should be amended in a revised version.

4. The captions should indeed give a clearer explanation of the figures. Owing to the page limit we preferred not to repeat explanations given in the main text.

Reviewer 2 ("Assigned_Reviewer_2")

1. The starting points of the manuscripts are three:

- the *sample-level* maximum-entropy method is increasingly being used in the neuroscientific literature (references below);

- this literature often generalizes results obtained with this method from a recorded sample to a whole area;

- worries have been expressed (eg Ganmor et al 2011, Roudi et al PlosCB 2009) about an excessive sample-size dependence of maximum-entropy results.

Unfortunately these three starting points are not clarified enough in our introduction; this should be amended in a revised version. We motivate the sample-size worries by simple probabilistic considerations, and provide alternative formulae to be used: Eq. (15) when the size of the full population is known, Eq. (19) when it is uncertain.

2. The sample approach is routinely used in the literature and we agree with the reviewer: "it is not even an option" if the recorded neurons are assumed to be a sample of a larger population. This is the message of the manuscript, unfortunately not clear enough. Its analysis is meant to explain why the sample approach is not an option and to propose two corrected formulae (Eqs 15, 19).

Our phrase "left for future work" was unfortunate: Eq. (19) for uncertain population size is actually an end result, ready to be used computationally if not analytically. What we left for future work was the analysis of its mathematical difference from (15) and (17). In a revised version of the paper we would add an example of distribution (19) to Figs 2 & 3.

We invite the reviewer to read also our responses 1, 2, 3 to the first reviewer.

3. Large space was dedicated to deriving the formulae of sampling without replacement. As mentioned on lines 42-45 this was on purpose because these old formulae are central in many neuroscientific problems and yet we have rarely seen them used in the neuroscience literature. We wanted to stress their importance.

But from those formulae the manuscript also presents novel results: Eqs (15) & (19), which can immediately be used instead of Eq. (17), currently used in the literature.

4. Equation (12) and its discussion (lines 113-129) are an excursion irrelevant to the rest of the paper, to the discussion of maximum-entropy and to the main equations we derive. We would eliminate this whole passage in a revised version.

5. We would have liked to present a Bayesian analysis of the problem, but the NIPS page limit prevented this. A measure of discrepancy, eg Kullback-Leibler divergence, between Eqs (15), (17), (19) could be added in a revised version.

Reviewer 3 ("Assigned_Reviewer_5")

We cordially thank the reviewer for the appreciative words. We want to add that our figures *do* use actual recorded neural activity data, but because of the double-blind review procedure we omitted this information, which we plan to add in the final version if the manuscript were accepted.

Sample references of maximum-entropy use in neuroscientific literature:
Martignon & al, Biol Cybern (1995)
Bohte & al, Neural Comp (2000)
Schneidman & al,  Nature (2006)
Shlens & al,  J Neurosci (2006)
Tkačik & al, arXiv:q-bio/0611072 (2006)
Macke & al, Neural Comp (2009)
Roudi & al, PLoS CB (2009)
Roudi & al, Front Comp Neurosci (2009)
Roudi & al, Phys Rev E (2009)
Tkačik & al, arXiv:09125409 (2009)
Macke & al, Tech Rep (2009)
Gerwinn & al, Front Comput Neurosci (2010)
Barreiro & al, arXiv:10112797 (2010)
Macke & al, NIPS (2011)
Macke & al, Phys Rev Lett (2011)
Ganmor & al, Proc Natl Acad Sci (2011)
Granot-Atedgi & al, PLoS CB (2013)
Macke & al, Entropy (2013)
Tkačik & al, Proc Natl Acad Sci (2014)
Mora & al, Phys Rev Lett (2015)
Shimazaki & al,  Sci Rep (2015)

### 2017-07-30 rebuttal3.txt

The author(s) thank the reviewers for their feedback, which is extremely useful for a revised version of the manuscript even in case of non-acceptance. Here are our comments point-by-point.

* Reviewer 1 (Assigned_Reviewer_1)

1. The sample-level maximum-entropy method has been repeatedly used and discussed in computational neuroscience at least since Bohte & al (2000). Unfortunately our Introduction did not clarify nor reference this context enough; this should be amended in a revised version. An unabridged bibliography is given at the end of this response and can be easily extended. The method is also used by non-experts; the manuscript aims to clarify implicit assumptions that users seem to be unaware of.

2. Our discussion starts from an observation: in the neuroscientific literature, several authors generalize conclusions drawn via maximum-entropy on recorded neurons, to whole areas the neurons are recorded from, eg retina or motor cortex. Unfortunately this observation was not clear in our Introduction. Whether such generalization makes biological sense is a difficult question to be analysed case-by-case. Our purpose is to give a statistician's warning: the sample-level equation (17) and the beyond-sample generalization, both typical of the literature, are incompatible. We propose two simple alternative equations (15, 19) compatible with the generalization.

The case of absolute ignorance (I'') is not used in the rest of the manuscript; we apologize for the confusion it creates. We would omit it in a revised version.

We invite the reviewer to read also our responses 1, 2 to the second reviewer.

3. The manuscript's principal equations are:

(15) to be used when a larger population is assumed and its size roughly known;

(17) to be used when no larger population is assumed. Most literature uses this equation but assumes a larger population;

(19) to be used when the the size of the larger population is uncertain.

Equations (15) & (19) are novel to our knowledge. We apologize for not emphasizing the role of the three equations above nor giving clear guidance to their use. This should be amended in a revised version.

4. The captions should be amended and give a clearer explanation of the figures. Owing to the page limit we chose not to repeat explanations given in the main text.

* Reviewer 2 (Assigned_Reviewer_2)

1. The manuscript's starting points are three:

- the *sample-level* maximum-entropy method is increasingly being used in the neuroscientific literature (refs below);

- this literature often generalizes results obtained via this method from a recorded sample to a whole area;

- worries have been expressed (eg Ganmor & al 2011, Roudi & al PlosCB 2009) about excessive sample-size dependence of maximum-entropy results.

We apologize for not clarifying enough these three starting points in our Introduction, which should be amended in a revised version. We aim to motivate the sample-size worries by simple probabilistic considerations, and to provide alternative correct formulae: Eq. (15) when the size of the full population is known, Eq. (19) when it is uncertain.

2. The sample approach is routinely used in the literature and we agree with the reviewer: "it is not even an option" if the recorded neurons are assumed to be a sample of a larger population. This is the message of the manuscript, unfortunately not clear enough. Its analysis is meant to explain why the sample approach is not an option and to propose two corrected formulae (Eqs 15, 19).

Our phrase "left for future work" was unfortunate: Eq. (19) for uncertain population size is actually an end result, ready to be used. What we left for future work was the analysis of its mathematical difference from (15) & (17). In a revised version we would add an example of distribution (19) to Figs 2 & 3.

We invite the reviewer to read also our responses 1-3 to the first reviewer.

3. Large space was given to deriving the formulae of sampling without replacement. As mentioned on lines 42-45 this was on purpose because these old formulae are central in many neuroscientific problems, yet we rarely see them used in the neuroscience literature. We wanted to stress their importance. But, starting from those formulae, the manuscript also presents novel results: Eqs (15) & (19), which can immediately be used instead of Eq. (17), currently used in the literature.

4. Eq. (12) and its discussion (lines 113-129) are an excursion irrelevant to the rest of the paper, to the discussion of maximum-entropy and to the main equations we derive. We would eliminate this whole passage in a revised version.

5. We would have liked to present a full Bayesian analysis of the problem, but the NIPS page limit prevents this. A measure of discrepancy, eg Kullback-Leibler divergence, between Eqs (15), (17), (19) would be added in a revised version.

* Reviewer 3 (Assigned_Reviewer_5)

We cordially thank the reviewer for the appreciative words. We want to add that our figures *do* use actual recorded neural activity data, but because of the double-blind review procedure we had to omit the related discussion at first. It would be added in the final version if the manuscript were accepted.

Sample references of maximum-entropy use in neuroscientific literature:
Martignon & al, Biol Cybern 1995
Bohte & al, Neural Comp 2000
Amari & al, Neural Comp 2003
Schneidman & al, Nature 2006
Shlens & al, J Neurosci 2006
Tkačik & al, arXiv:q-bio/0611072 2006
Mcdonald & al, NIPS 2009
Macke & al, Neural Comp 2009
Roudi & al, PLoS CB 2009
Roudi & al, Front Comp Neurosci 2009
Roudi & al, Phys Rev E 2009
Tkačik & al, arXiv:0912.5409 2009
Macke & al, Tech Rep 2009
Gerwinn & al, NIPS 2009
Barreiro & al, BMC Neurosci 2010
Macke & al, NIPS 2011
Macke & al, Phys Rev Lett 2011
Ganmor & al, Proc Natl Acad Sci 2011
Granot-Atedgi & al, PLoS CB 2013
Macke & al, Entropy 2013
Tkačik & al, Proc Natl Acad Sci 2014
Mora & al, Phys Rev Lett 2015
Shimazaki & al, Sci Rep 2015

### 2017-12-04 maxNt.tex
results

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-19T15:42:30+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\usepackage[%final,%
nonatbib]{nips_2017}

@@

\newcommand*{\headtitle}{\pdftitle} \newcommand*{\pdfauthor}{%P.G.L. Porta Mana, V. Rostami, E. Torre
Anonymous Author(s)}
\usepackage{newtxmath}
%\usepackage{pifont}
%\usepackage{fontawesome}
\usepackage[T1]{fontenc} 
\input{glyphtounicode} \pdfgentounicode=1
\usepackage[utf8]{inputenx}
%\usepackage{newunicodechar}
% \newunicodechar{Ĕ}{\u{E}}
% \newunicodechar{ĕ}{\u{e}}
% \newunicodechar{Ĭ}{\u{I}}
% \newunicodechar{ĭ}{\u{\i}}
% \newunicodechar{Ŏ}{\u{O}}
% \newunicodechar{ŏ}{\u{o}}
% \newunicodechar{Ŭ}{\u{U}}
% \newunicodechar{ŭ}{\u{u}}
% \newunicodechar{Ā}{\=A}
% \newunicodechar{ā}{\=a}
% \newunicodechar{Ē}{\=E}
% \newunicodechar{ē}{\=e}
% \newunicodechar{Ī}{\=I}
% \newunicodechar{ī}{\={\i}}
% \newunicodechar{Ō}{\=O}
% \newunicodechar{ō}{\=o}
% \newunicodechar{Ū}{\=U}
% \newunicodechar{ū}{\=u}
% \newunicodechar{Ȳ}{\=Y}
% \newunicodechar{ȳ}{\=y}

@@

\author{
  P.G.L. Porta Mana\thanks{Equally contributing first authors}\\Independent researcher\\\texttt{pgl@portamana.org}
  \And
  V. Rostami$^*$\\Forschungszentrum J{\"u}lich INM-6\\Germany\\\texttt{v.rostami@fz-juelich.de}
  \And
E. Torre\\ETH Z{\"u}rich\\Switzerland\\
\texttt{torre@ibk.baug.ethz.ch}
  % David S.~Hippocampus\thanks{Use footnote for providing further
  %   information about author (webpage, alternative
  %   address)---\emph{not} for acknowledging funding agencies.} \\
  % Department of Computer Science\\
  % Cranberry-Lemon University\\
  % Pittsburgh, PA 15213 \\
  % \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

The sample distribution obtained from \me\ at the sample level will
therefore likely miss important features present in the one obtained at the
population level, like additional modes or particular tail behaviour.
\begin{figure}[!t]
\centering
\includegraphics[width=0.9\linewidth]{different_maxent_pop_sample_200_realdata_2mom.pdf}%
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at the population
  level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:app_maxent_pop_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:app_maxent_sample}, with $N=5000$,
  $n=200$, constraints $\expe{\yxs}=0.0478$, $\expe{\yxxs}=0.00257$.}
\label{fig:diff_maxent_pop_sample}
\end{figure}%maxent_pop_or_sample.nb
% \end{wrapfigure}
\begin{figure}[!t]
\centering
\includegraphics[width=0.9\linewidth]{different_maxent_pop_sample_200_realdata_4mom.pdf}
% 
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at
  the population level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:app_maxent_pop_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:app_maxent_sample}, with $N=5000$,
  $n=200$, constraints $\expe{\yxs}=0.0478$, $\expe{\yxxs}=0.00257$,
  $\expe{\sav{\yx\yx\yx}}=1.48\times10^{-4}$,
  $\expe{\sav{\yx\yx\yx\yx}}=8.81\times 10^{-6}$.}
\label{fig:diff_maxent_pop_sample_realdata}
\end{figure}%maxent_pop_or_sample.nb
We show two examples of this discrepancy in
\figs~\ref{fig:diff_maxent_pop_sample}
and~\ref{fig:diff_maxent_pop_sample_realdata}, for $N=5000$, $n=200$, and
constraint functions of the form
$\yf(\yxs)=(\yxs,\yxxs,\dotsc)\equiv\bigl( \yxs,
\raisebox{0pt}[0pt][1ex]{}\binom{n\yxs}{2}/\binom{n}{2},\dotsc \bigr)$,
equivalent to moments constraints. The constraint values used in these
examples, reported in the figure captions, have neurobiologically realistic
values \cite{rostamietal2016}.

@@

This fact can be significant for recent works
\citep[\eg,][]{schneidmanetal2006,shlensetal2006,tkaciketal2006,marreetal2009,tkaciketal2009,ganmoretal2011,shimazakietal2012,tkaciketal2013,shimazakietal2015}
in which a maximum-entropy probability distribution with second- or
third-moment constraints is assigned to relatively small subnetworks
($n < 200$) of neurons. If we assume that such subnetwork is part of a
larger network, and assume the condition of symmetry~\eqref{noeq:homog_math},
then the larger network \emph{cannot} be assigned a maximum-entropy
distribution with the same number of constraints. Vice versa, if we assign
such a maximum-entropy distribution to the larger network, then none of its
subnetwork of enough large size $n$ can be assigned a similar
maximum-entropy distribution. See ref.~\citep{rostamietal2016} for a
broader discussion of this fact and of its consequences.

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-12-04T11:34:56+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\usepackage[final,%
nonatbib]{nips_2017}

@@

\newcommand*{\headtitle}{\pdftitle} \newcommand*{\pdfauthor}{P.G.L. Porta Mana, V. Rostami, E. Torre}
\usepackage{newtxmath}
%\usepackage{pifont}
%\usepackage{fontawesome}
\usepackage[T1]{fontenc} 
\input{glyphtounicode} \pdfgentounicode=1
\usepackage[utf8]{inputenx}
%\usepackage{newunicodechar}
% \newunicodechar{Ĕ}{\u{E}}
% \newunicodechar{ĕ}{\u{e}}
% \newunicodechar{Ĭ}{\u{I}}
% \newunicodechar{ĭ}{\u{\i}}
% \newunicodechar{Ŏ}{\u{O}}
% \newunicodechar{ŏ}{\u{o}}
% \newunicodechar{Ŭ}{\u{U}}
% \newunicodechar{ŭ}{\u{u}}
% \newunicodechar{Ā}{\=A}
% \newunicodechar{ā}{\=a}
% \newunicodechar{Ē}{\=E}
% \newunicodechar{ē}{\=e}
% \newunicodechar{Ī}{\=I}
% \newunicodechar{ī}{\={\i}}
% \newunicodechar{Ō}{\=O}
% \newunicodechar{ō}{\=o}
% \newunicodechar{Ū}{\=U}
% \newunicodechar{ū}{\=u}
% \newunicodechar{Ȳ}{\=Y}
% \newunicodechar{ȳ}{\=y}

@@

\author{
  P.G.L. Porta Mana\\\texttt{mana@kth.org}
  \And
  V. Rostami$^*$\\\texttt{v.rostami@fz-juelich.de}
  \And
E. Torre\\\texttt{torre@ibk.baug.ethz.ch}
  % David S.~Hippocampus\thanks{Use footnote for providing further
  %   information about author (webpage, alternative
  %   address)---\emph{not} for acknowledging funding agencies.} \\
  % Department of Computer Science\\
  % Cranberry-Lemon University\\
  % Pittsburgh, PA 15213 \\
  % \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

@@

The sample distribution obtained from \me\ at the sample level will
therefore likely miss important features present in the one obtained at the
population level, like additional modes or particular tail behaviour.
\begin{figure}[!t]
\centering
\includegraphics[width=0.9\linewidth]{different_maxent_pop_sample_200_realdata_2mom.pdf}%
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at the population
  level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:app_maxent_pop_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:app_maxent_sample}, with $N=5000$,
  $n=200$, constraints $\expe{\yxs}=0.0478$, $\expe{\yxxs}=0.00257$.}
\label{fig:diff_maxent_pop_sample}
\end{figure}%maxent_pop_or_sample.nb
% \end{wrapfigure}
\begin{figure}[!t]
\centering
\includegraphics[width=0.9\linewidth]{different_maxent_pop_sample_200_realdata_4mom.pdf}
% 
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at
  the population level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:app_maxent_pop_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:app_maxent_sample}, with $N=5000$,
  $n=200$, constraints $\expe{\yxs}=0.0478$, $\expe{\yxxs}=0.00257$,
  $\expe{\sav{\yx\yx\yx}}=1.48\times10^{-4}$,
  $\expe{\sav{\yx\yx\yx\yx}}=8.81\times 10^{-6}$.}
\label{fig:diff_maxent_pop_sample_realdata}
\end{figure}%maxent_pop_or_sample.nb
We show two examples of this discrepancy in
\figs~\ref{fig:diff_maxent_pop_sample}
and~\ref{fig:diff_maxent_pop_sample_realdata}, for $N=5000$, $n=200$, and
constraint functions of the form
$\yf(\yxs)=(\yxs,\yxxs,\dotsc)\equiv\bigl( \yxs,
\raisebox{0pt}[0pt][1ex]{}\binom{n\yxs}{2}/\binom{n}{2},\dotsc \bigr)$,
equivalent to moments constraints. The constraint values used in these
examples, reported in the figure captions, have neurobiologically realistic
values \cite{rostamietal2016_r2017}.

@@

This fact can be significant for recent works
\citep[\eg,][]{schneidmanetal2006,shlensetal2006,tkaciketal2006,marreetal2009,tkaciketal2009,ganmoretal2011,shimazakietal2012,tkaciketal2013,shimazakietal2015}
in which a maximum-entropy probability distribution with second- or
third-moment constraints is assigned to relatively small subnetworks
($n < 200$) of neurons. If we assume that such subnetwork is part of a
larger network, and assume the condition of symmetry~\eqref{noeq:homog_math},
then the larger network \emph{cannot} be assigned a maximum-entropy
distribution with the same number of constraints. Vice versa, if we assign
such a maximum-entropy distribution to the larger network, then none of its
subnetwork of enough large size $n$ can be assigned a similar
maximum-entropy distribution. See ref.~\citep{rostamietal2016_r2017} for a
broader discussion of this fact and of its consequences.
